Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-26 paper.qmd
Added 2D layouts of Five Gau

@@

@@

@@

>>>>

tsne_gau <- tsne_gau_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2)) +
  geom_point(alpha=0.3, color = "#000000")

@@

umap_gau <- umap_gau_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.3, color = "#000000")

@@

pacmap_gau <- pacmap_gau_scaled |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2)) +
  geom_point(alpha=0.3, color = "#000000")

@@

```{r}
#| label: fig-five-gau-nldr-layouts
#| fig-height: 5
#| fig-width: 15
#| fig-pos: H
#| fig-cap: "(a) tSNE, (b) UMAP, and (c) PaCMAP"

tsne_gau + umap_gau + pacmap_gau +
  plot_layout(ncol = 3)
```
